\chapter{Docker}
\label{ch:docker}
\newthought{Docker is} 'an open platform for developingm shipping and running applications'. It is a convenient way for us to provide all of the dependencies and the latest release source code so that you can use the ginarn tool kit straight out of the box.
%
In order for this to work, you will first need to install the docker engine onto your local machine. If you are running a different operating system instructions on how to install docker can be found at \href{https://docs.docker.com/get-docker/}{docker desktop downlod link}, these also include alternative methods of installing on ubuntu and has links to recommended best practices.
%
To find more information on docker have a look at the \href{https://docs.docker.com/get-started/}{getting started guide} procided by docker.
%
\section{Ubuntu Docker dependency installation guide}
If you are running ubuntu, you can install a docker engine. A summary of the commands to download and install docker involve setting up the ubuntu repository system to link with the docker repsotory are given below.

\begin{lstlisting}[language=bash]
$ sudo apt -y update
$ sudo apt -y install \
apt-transport-https \
ca-certificates \
curl \
gnupg \
lsb-release
\end{lstlisting}

Add the dockers official GPG key:
\begin{lstlisting}[language=bash]
$ curl -fsSL https://download.docker.com/linux/ubuntu/gpg | sudo gpg --dearmor -o /usr/share/keyrings/docker-archive-keyring.gpg
$ echo \
"deb [arch=amd64 signed-by=/usr/share/keyrings/docker-archive-keyring.gpg] https://download.docker.com/linux/ubuntu $(lsb_release -cs) stable" | sudo tee /etc/apt/sources.list.d/docker.list > /dev/null
\end{lstlisting}
%
Then update the repository management system and install the packages.
%
\begin{lstlisting}[language=bash]
$ sudo apt-get update
$ sudo apt-get install docker-ce docker-ce-cli containerd.io
\end{lstlisting}

Verify that the Docker engine is installed correctly by running the \emph{hello-world} image.

Then you will need to change the ownership:
\begin{lstlisting}[language=bash]
$ sudo usermod -aG docker root
\end{lstlisting}

\section{Using Docker}

Once you have docker installed on your local machine you will need to download our image for ginarn:
\begin{lstlisting}[language=bash]
$ docker pull gamichaelmoore/ginarn-base-ubuntu-20.04
\end{lstlisting}








