\chapter{PEA YAML Configuration}

\label{ch:pea_yaml_configuration}

\section{PEA processing options}
%
%
\section{Input File Options}
\begin{lstlisting}[language=yaml,caption=yaml input files configuration example]
input_files:

root_input_directory: /data/acs/pea/proc/exs/products

atxfiles:      [  igs14_2045_plus.atx                       ]  # Antenna models
snxfiles:      [  igs19P2062.snx                            ]  # meta data and apriori coords
blqfiles:      [  OLOAD_GO.BLQ                              ]  # ocean loading is applied
navfiles:      [  brdm1990.19p                              ]  # gnss broadcast file
sp3files:      [  gag20624.sp3                              ]  # precise orbit data 
erpfiles:      [  igs19P2062.erp                            ]  # earth orintation parameters
#dcbfiles:      [  CAS0MGXRAP_20191990000_01D_01D_DCB.BSX   ]  # monthly DCB file
#clkfiles:     [  jpl20624.clk                              ]  # satellie and receiver clock 
orbfiles:      [  gag20624_orbits_partials.out              ]  # need this when estimating orbits (overrides .sp3 file)
\end{lstlisting}

\section{RINEX station data}

%RINEX2 and RINEX3 data
There are numerous ways that the \emph{pea} can access GNSS RINEX observations to process. You can specify individual rinex files to process, set it up so that it will search a particular directory, or you can use a command line flag \emph{-rnx <rnxfilename>} to add an additional file to process. The data should be uncompressed (gunzipped, and not in hatanaka format), that is the \emph{pea} expecting to just accept RINEX format]. 
%
\begin{lstlisting}[language=yaml,caption=pea yaml processing one station example]
station_data:

	root_stations_directory: /data/ginan/proc/data

	rnxfiles:
		- ALIC00AUS_R_20191990000_01D_30S_MO.rnx                          
\end{lstlisting}\label{lst:pea-yaml-realtime-single-station}

%
To process one RINEX file, you need to first specify the root dircetory of where the data is being stored in \emph{root\_stations\_directory}, and then the name of the RINEX file as a single entry under \emph{rnxfiles:}, as shown in the listing~ref{lst:pea-yaml-single-station}. 
%
\begin{lstlisting}[language=bash,caption=Example showing how to add a RINEX file to the processing list form the command line]
$ pea --rnx CAS100ATA_R_20191990000_01D_30S_MO.rnx
\end{lstlisting}
%
If you wanted to process another file, located in the same \emph{root\_stations\_directory}, this can be achieved at the command line using the \emph{-rnx \textless rnxfilename \textgreater} flag, see listing~ref{lst:pea-yaml-add-station}.
%
\begin{lstlisting}[language=yaml,caption=yaml input files configuration example]
station_data:

root_stations_directory: /data/acs/pea/proc/exs/data

rnxfiles:
- "*.rnx"                           #- searching all in file_root directory
\end{lstlisting}

\section{Real-time streams}
To process data in real-time you will need to set up the location, username annd password for the caster that you will be obtaining the input data streams from in the configuration file.

The pea supports obtaining streams from casters that use NTRIP 2.0 over http and https.

%TODO check I believe we can do multiple casters for input At the moment the pea is able to connect to one caster for input data streams, and a different caster for the output of correction messages.

\begin{lstlisting}[language=yaml,caption=yaml input files configuration example]
station_data:

	stream_root: "http://<usedname>:<password>@auscors.ga.gov.au:2101/"

	streams:
		- BCEP00BKG0
		- SSRA00CNE0
		- STR100AUS0
\end{lstlisting}
%
As shown in listing:~\ref{lst:pea-yaml-realtime-single-station}, the caster url, username and password are specified within double quotes with the \emph{stream\_root} tag. In this example the streams are being obtained from the auscors caster run by Geoscience Australia. 
The broadcast information is being obtained from the stream \emph{BCEP00BKG0} being supplied by BKG, and corrections to the utlra-rapid predicted orbit are being obtained from the stream \emph{SSRA00CNE0}. 
The real-time data being processed is for the continuous GNSS station located at Mount Stromlo obtained from the stream \emph{STR100AUS0}.

You can test your username and password is working correctly by running the curl command:
\begin{lstlisting}[language=bash]
curl https://ntrip.data.gnss.ga.gov.au/ALIC00AUS0 -H "Ntrip-Version: NTRIP/2.0" -i  --output - -u <user>
\end{lstlisting}
%
\section{output files:}
\begin{lstlisting}[language=yaml,caption=yaml input files configuration example]
output_files:

root_output_directory:          /data/acs/pea/output/<CONFIG>/

log_level:                      warn                             #debug, info, warn, error as defined in boost::log

output_trace:                   true
trace_level:                    2
trace_directory:                ./
trace_filename:                 <CONFIG>-<STATION><YYYY><DDD><HH>.TRACE

output_residuals:               true

output_persistance:             false
input_persistance:              false
persistance_directory:          ./
persistance_filename:           <CONFIG>.persist

output_config:                  false

output_summary:                 true
summary_directory:              ./
summary_filename:               PEA<YYYY><DDD><HH>.SUM

output_ionex:                   false
ionex_directory:                ./
ionex_filename:                 IONEX.ionex
iondsb_filename:                IONEX.iondcb

output_clocks:                  true
clocks_directory:               ./
clocks_filename:                <CONFIG>.clk
output_AR_clocks:               true

output_sinex:                   true
sinex_directory:                ./
\end{lstlisting}

\section{output options:}

\begin{lstlisting}[language=yaml,caption=yaml input files configuration example]
output_options:

config_description:             EX03_AR
analysis_agency:                GAA
analysis_center:                Geoscience Australia
analysis_program:               AUSACS
rinex_comment:                  AUSNETWORK1
\end{lstlisting}

\section{processing Options}

\begin{lstlisting}[language=yaml,caption=yaml input files configuration example]
processing_options:

#start_epoch:               2019-07-18 00:00:00
#end_epoch:                 2017-03-29 23:59:30
#max_epochs:                300        #0 is infinite
epoch_interval:             30          #seconds

process_modes:
user:                   false
network:                true
minimum_constraints:    false
rts:                    false
ionosphere:             false
unit_tests:             false

process_sys:
gps:            true
#glo:           true
gal:            false
#bds:           true

elevation_mask:     10   #degrees

tide_solid:         true
tide_pole:          true
tide_otl:           true

phase_windup:       true
reject_eclipse:     true            #  reject observation during satellite eclipse periods
raim:               true
antexacs:           true

cycle_slip:
thres_slip: 0.05

max_inno:   0
max_gdop:   30

troposphere:
model:      gpt2    #vmf3
gpt2grid:   gpt_25.grd
#vmf3dir:    grid5/
#orography:  orography_ell_5x5

ionosphere:
corr_mode:      iono_free_linear_combo
iflc_freqs:     l1l2_only   #any l1l2_only l1l5_only

pivot_station:        "USN7"
#pivot_satellite:      "G01"

code_priorities: [  L1C, L1P, L1Y, L1W, L1M, L1N, L1S, L1L,
L2W, L2P, L2Y, L2C, L2M, L2N, L2D, L2S, L2L, L2X,
L5I, L5Q, L5X]
\end{lstlisting}

\section{Network filter parameters}
\begin{lstlisting}[language=yaml,caption=yaml input files configuration example]
network_filter_parameters:

process_mode:               kalman      #lsq
inverter:                   LLT         #LLT LDLT INV

max_filter_iterations:      3
max_filter_removals:        3

rts_lag:                    -1      #-ve for full reverse, +ve for limited epochs
rts_directory:              ./
rts_filename:               <CONFIG>-Orbits.rts
\end{lstlisting}

\section{Default filter parameters: stations}

\begin{lstlisting}[language=yaml,caption=yaml input files configuration example]
default_filter_parameters:

	stations:	
		error_model:        elevation_dependent         #uniform elevation_dependent
			code_sigmas:        [0.30]
			phase_sigmas:       [0.003]
		pos:
			estimated:          false
			sigma:              [1.0]
			proc_noise:         [0]
			#apriori:                                   # taken from other source, rinex file etc.
			#frame:              xyz #ned
			#proc_noise_model:   Gaussian
			#clamp_max:          [+0.5]
			#clamp_min:          [-0.5]
		clk:
			estimated:          true
			sigma:              [0]
			proc_noise:         [1.8257418583505538]
			#proc_noise:         [10]
			#proc_noise_model:   Gaussian
		clk_rate:
			estimated:          false
			sigma:              [10]
			proc_noise:         [1e-4]
			#clamp_max:          [1000]
			#clamp_min:          [-1000]
		amb:
			estimated:          true
			sigma:              [100]
			proc_noise:         [0]
		trop:
			estimated:          true
			sigma:              [0.1]
			proc_noise:         [0.000083333]
		trop_grads:
			estimated:          false
			sigma:              [0.1]
			proc_noise:         [0.0000036]
\end{lstlisting}

\section{Default filter parameters: satellites}

\begin{lstlisting}[language=yaml,caption=yaml input files configuration example]
    satellites:

		clk:
			estimated:          true
			sigma:              [0]
			proc_noise:         [0.03651483716701108]
		
		clk_rate:
			estimated:          false
			sigma:              [0.01]
			proc_noise:         [1e-6]
		
		orb:
			estimated:          true
			sigma:              [5e-1, 5e-1, 5e-1, 5e-3, 5e-3, 5e-3, 5e-1]
\end{lstlisting}

\section{Default filter parameters: eop}

\begin{lstlisting}[language=yaml,caption=yaml input files configuration example]
	eop:
		estimated:  true
		sigma:      [30]
		#proc_noise: [0.0000036]

\end{lstlisting}


\section{Ambiguity Resolution Options}
%

\begin{lstlisting}[language=yaml,caption=yaml ambiguity configuration example]
	ambiguity_resolution_options:
		Min_elev_for_AR:            15.0
		GPS_amb_resol:              true
		GAL_amb_resol:              false
		#Set_size_for_lambda:        10

	WL_mode:                    iter_rnd        # AR mode for WL: off, round, iter_rnd, bootst, lambda, lambda_alt, lambda_al2, lambda_bie
		WL_succ_rate_thres:         0.9999
		WL_sol_ratio_thres:         3.0
		WL_procs_noise_sat:         0.00001
		WL_procs_noise_sta:         0.0001

	NL_mode:                    iter_rnd        # AR mode for WL: off, round, iter_rnd, bootst, lambda, lambda_alt, lambda_al2, lambda_bie
		NL_succ_rate_thres:         0.9999
		NL_sol_ratio_thres:         3.0
		NL_proc_start:              86310

	bias_read_mode:             30              # +1: read DSB biases, +2: read OSB biases, +4: read code biases, +8: read phase biases, +16: read satellite bias, +32: read station bias,
		bias_output_rate:           300.0
\end{lstlisting}





















\chapter{PEA Configuration File - YAML}
	
The PEA processing engine uses a single yaml file for configuration of all processing options.

\section{YAML Syntax}
The yaml format allows for heirarchical, self descriptive configurations of parameters, and has a straightforward syntax.

White-space (indentation) is used to specify heirarchies, with each level typically indented with 4 space characters.

Colons (:) are used to separate configuration keys from their values.

Lists may be created by either appending multiple values on a single line, wrapped in square brackets and separated by commas, or, by adding each value on a separate indented line with a dash before the value.

Adding a hash symbol (\#) to a line will render the remainder of the line as a comment to be ignored by the parser.

Strings with special characters or spaces should be wrapped in quotation marks.

You will see all of these used in the example configuration files, but the files may be re-ordered, or re-formatted to suit your application.

\section{Default Values}

Many processing options have default values associated with them. To prevent repetition, and to ensure that the values are reported correctly, these values may be viewed in the acsConfig.hpp file within the source code directories.

\section{input\_files:}

This section of the yaml file specifies the lists of files to be used for general metadata inputs, and inputs of external product data.

\begin{lstlisting}[language=yaml,caption=A typical input\_files section]
# Example
input_files:

	root_input_directory: /data/acs/pea/proc/exs/products/
	
	atxfiles:   [ igs14_2045_plus.atx                                ]
	snxfiles:   [ igs19P2062.snx                                     ]
	blqfiles:   [ OLOAD_GO.BLQ                                       ]  
	navfiles:   [ brdm1990.19p                                       ]  
	orbfiles:   [ orb_partials/gag20624_orbits_partials_new.out      ]  
	sp3files:   [ "*.sp3"                                            ]
	clkfiles:   [ jpl20624.clk                                       ]  
	erpfiles:   [ igs19P2062.erp                                     ]  
	dcbfiles:   [ CAS0MGXRAP_20191990000_01D_01D_DCB.BSX             ] 
	bsxfiles:   []
	ionfiles:   [] 
\end{lstlisting}

\subsection{Globbing}
Files may be specified individually, as lists, or by searching available files using a globbed filename using the star character (*)

\subsection{root\_input\_directory:}
This specifies a root directory to be prepended to all other file paths specified in this section. For file paths that are absolute, (ie. starting with a /), this parameter is not applied.

\subsection{atxfiles:}
A list of ANTEX files to be used in processing. These may supply the antenna parameters to be used by satellites and receivers.

\subsection{snxfiles:}
A list of SINEX files to be used in processing. These may supply the initial positions and other metadata for receivers.

\subsection{blqfiles:}
A list of BLQ files to be used in processing. These may supply the ocean tide loading data.

\subsection{navfiles:}
A list of NAV files to be used in processing. These may supply the basic broadcast ephemerides for satellites.

\subsection{orbfiles:}
A list of ORB files to be used in processing. These may supply the PEA with orbital and ratiation pressure data from the Ginan's POD module, allowing precise orbit data to be passed between the two pieces of software.

\subsection{sp3files:}
A list of SP3 files to be used in processing. These may supply the ephemerides for higher precision processing.

\subsection{clkfiles:}
A list of CLK files to be used in processing. These may supply the clock offsets for satellites and receivers for higher precision processing.

\subsection{erpfiles:}
A list of ERP files to be used in processing. These may supply the earth rotation parameter information.

\subsection{dcbfiles:}
A list of DCB files to be used in processing. These may supply the differential code biases to assist with ambiguity resolution.

\subsection{bsxfiles:}
A list of BSINEX files to be used in processing. These may supply biases to assist with ambiguity resolution.

\subsection{ionfiles:}
A list of ION files to be used in processing. These may supply the ionospheric modelling parameters for single frequency processing.










\section{output\_files:}
This section of the yaml file specifies options to enable outputs and specify file locations.

An example of this section follows:
\begin{lstlisting}[language=yaml,caption=output\_files:]
output_files:

root_output_directory:          /data/acs/ginan/examples/<CONFIG>/

output_trace:                   true
trace_level:                    3
trace_directory:                ./
trace_filename:                 <CONFIG>-<STATION><LOGTIME>.TRACE

output_residuals:               false

output_config:                  true

output_summary:                 false
summary_directory:              ./
summary_filename:               <CONFIG>-<YYYY><DDD><HH>.SUM

output_clocks:                  true
clocks_directory:               ./
clocks_filename:                <CONFIG>.clk
\end{lstlisting}

\subsection{Wildcard Tags}
Output filenames can include wildcards wrapped in < > brackets to allow more generic names to be used. While processing, these tags are replaced with details gathered from processing, and allows for automatic generation of, for example, hourly output files.

\subsection{\textless CONFIG\textgreater}
This is replaced with the 'config\_description' value entered in the yaml file.
\subsection{\textless STATION\textgreater}
This is replaced with the 4 character station id of each station that generates a trace file.
\subsection{\textless LOGTIME\textgreater}
This is replaced with the (rounded) time of the epochs within the trace file.

If trace file rotation is configured for 1 hour, the <LOGTIME> wildcard will be rounded down to the closest hour, and subsequently change value once per hour and generate a separate output file for each hour of processing.

\subsection
{\textless DDD\textgreater,
\textless D\textgreater, 
\textless WWWW\textgreater, 
\textless YYYY\textgreater, 
\textless YY\textgreater, 
\textless MM\textgreater, 
\textless DD\textgreater, 
\textless HH\textgreater}
These are replaced with the components of time of the start epoch.


\subsection{root\_output\_dir:}
This specifies a root directory to be prepended to all other file paths specified in this section. For file paths that are absolute, (ie. starting with a /), this parameter is not applied.

\subsection{[X]\_directory:}
Directory to output file [X] to, where [X] are the features below. May contain wildcard tags. May be relative to root\_output\_dir, or absolute. If the directory does not exist, it will be created.

trace\_directory, summary\_directory, clocks\_directory, ionex\_directory, biasSinex\_directory, sinex\_directory, persistance\_directory

\subsection{[X]\_filename:}
Filename to use for output of [X]. May contain wildcard tags. File will be created or overwritten if it already exists.

trace\_filename, summary\_filename, clocks\_filename, ionex\_filename, biasSinex\_filename, sinex\_filename, persistance\_filename

\subsection{trace\_level:}
Integer from 0-5 to specify verbosity of trace outputs. (5 - print everything)

\subsection{trace\_rotate\_period, trace\_rotate\_period\_units:}
Granularity of length of time used for \textless LOGTIME\textgreater tags. These parameters may be used such that the filename of an output will change intermittently, and thus distribute the output over multiple files.

The \textless LOGTIME\textgreater tag is updated according to the epoch time, not the current clock time.

trace\_rotate\_period must be a numeric value, and trace\_rotate\_period\_units may be one of seconds (default), minutes, hours, days, weeks, years, (with or without plural s).

\subsection{output\_residuals:}
Boolean to print the residuals from kalman filter operation to relevant trace files.

\subsection{output\_config:}
Boolean to print a copy of the yaml file to the top of each trace file. This may assist with keeping a record of the parameters used to generate the particular results contained in the file.

\subsection{output\_trace:}
Boolean to generate per-station trace files.

\subsection{output\_summary:}
Boolean to generate a network summary file.

\subsection{output\_clocks:}
Boolean to generate RINEX formatted clock files from processed data.

\subsection{output\_AR\_clocks:}
Boolean to specify that the ambiguity resolved version of clocks should be output if output\_clocks is enabled.

\subsection{output\_ionex:}
Boolean to generate an IONEX file from processed ionosphere data.

\subsection{output\_ionstec:}
Boolean to generate an IONSTEC file from processed ionosphere data.

\subsection{output\_biasSINEX:}
Boolean to generate a biasSINEX from processed network data.

\subsection{output\_sinex:}
Boolean to generate a sinex file containing processed solutions, and the metadata used to generate them.

\subsection{output\_persistance:}
Boolean to save the network filter state, and navigation and ephemerides structure to disk once per epoch. For realtime processing where ephemerides are sourced from a a stream over several minutes, this may enable quicker start-up if the processor is restarted.

\subsection{input\_persisance:}
Boolean to try to load a saved filter and navigation structure from disk.

\subsection{output\_mongo\_measurements:}
Boolean to output kalman filter measurements and residuals to a mongo database.

\subsection{output\_mongo\_states:}
Boolean to output the results of kalman filter processing to a mongo database.

\subsection{output\_mongo\_logs:}
Boolean to output timestamped log data from the console to a mongo database.

\subsection{output\_mongo\_metadata:}
Boolean to output timestamped metadata from processing to a mongo database. (unimplemented)

\subsection{delete\_mongo\_history:}
Boolean to delete a previous database using the same <CONFIG> tag before processing, to prevent collisions.

\subsection{mongo\_uri:}
The URL to the location of the mongo database server.









\section{station\_data:}
This section specifies the sources of observation data to be used in positioning.

It may consist of RINEX files, or RTCM streams, which are specified as follows:
\subsubsection{Post processing:}

\begin{lstlisting}[language=yaml,caption=station\_data:]
# post processing example
station_data:
	root_stations_directory: /data/acs/ginan/examples/data
	rnxfiles:
		- "ALIC*.rnx"
		- "BAKO*.rnx"
\end{lstlisting}


\subsection{root\_stations\_directory:}
This specifies a root directory to be prepended to all other file paths specified in this section. For file paths that are absolute, (ie. starting with a /), this parameter is not applied.

\subsection{rnxfiles:}
This is a list of RINEX files to be used for observation data. The first 4 characters of the filename are used as the receiver ID.

If multiple files are supplied with the same ID, they are all processed in sequence - according to the epoch times specified within the files. In this case, it is advisible to correctly specify the start\_epoch for the filter, or the first epoch in the first file will likely be used.

\subsection{rtcmfiles:}
This is a list of RTCM binary files to be used for observation data. The first 4 characters of the filename are used as the receiver ID.

This can be used to read data that has been saved from a stream for later testing. There may be synchronisation issues when multiple such files are used.

\subsubsection{Real-time processing:}
\begin{lstlisting}[language=yaml,caption=station\_data:]
# realtime streaming example
station_data:
	
	stream_root: "https://USERNAME:password@ntrip.data.gnss.ga.gov.au/"
	
	obs_streams:
	- BLCK00AUS0
	- BBDH00AUS0
	- BOMB00AUS0
	- BLGL00AUS0
	
	nav_streams:
	- SSR100AUS0
\end{lstlisting}


\subsection{stream\_root:}
This specifies a root url to be prepended to all other streams specified in this section. If the streams used have individually specified root urls, usernames, or passwords, this should not be used.

\subsection{obs\_streams:}
This is a list of RTCM streams to read realtime data from. The first 4 characters of the filename are used as the receiver ID.

In combination with the stream\_root parameter, they may require a username, password, port and mountpoint.

The streams in this section are processed for observations from receivers.

\subsection{nav\_streams:}
This is a list of RTCM streams to read realtime data from. 

In combination with the stream\_root parameter, they may require a username, password, port and mountpoint.

The streams in this section are processed separately from observations, and will typically be used for receiving SSR messages or other navigational data from an external service.
















\section{processing\_options:}

This sections specifies the extent of processing that is performed by the engine.

\subsection{epoch\_interval:}
Increment in nominal epoch time for each processing epoch. This parameter may be used to sub-sample datasets by using an epoch\_interval that is a multiple of the dataset's internal interval between epochs.

\subsection{start\_epoch}
Nominal time of the first epoch to process. Time is formatted as YYYY-MM-DD HH:MM:SS.
This parameter may be left undefined to use the first available data point.

\subsection{end\_epoch}
Maximum nominal time of the last epoch to process. This parameter may be left undefined.

\subsection{max\_epochs:}
Maximum epochs to process before completion. This parameter may be left undefined.

\subsection{process\_modes:}

\begin{lstlisting}[language=yaml,caption=process\_modes:]
process_modes:
    user:                   true
    network:                false
    minimum_constraints:    false
    rts:                    false
    ionosphere:             false
\end{lstlisting}

\subsection{user:}
Boolean to process all stations individually. Typically used for determining position of individual receivers. See TODO
\subsection{network:}
Boolean to process all stations in a single filter. May be used for determination of orbits, clocks, etc. See TODO
\subsection{minimum\_constraints:}
Boolean to apply a rigid transformation to the results of the network filter after completion. See TODO
\subsection{ionosphere:}
Boolean to compute an ionosphere model from observations. See TODO
\subsection{unit\_tests:}
Boolean to run tests to compare intermediate values during processing to stored results. See TODO

\subsection{process\_sys:}
\begin{lstlisting}[language=yaml,caption=process\_sys:]
process_sys:
    gps:            true
    glo:            false
    gal:            false
    bds:            false
\end{lstlisting}

\subsubsection{gps:}
\subsubsection{glo:}
\subsubsection{gal:}

\subsection{elevation\_mask:}
Minimum elevation required for observations to be used, measured in degrees.

\subsection{ppp\_ephemeris:}
Option to specify source of satellite ephemeris used in PPP processing. Sources are

broadcast,
precise,
precise\_com,
sbas,
ssr\_apc,
ssr\_com

\subsection{tide\_solid:}
Boolean to apply solid tide model to station positions.
\subsection{tide\_otl:}
Boolean to apply ocean tide loading model to station positions.
\subsection{tide\_pole:}
Boolean to apply pole tide model to station positions.
\subsection{phase\_windup}
Boolean to apply phase windup model to satellite phase measurements.
\subsection{reject\_eclipse}
Boolean to exclude eclipsed satellites from processing.
\subsection{raim}
Boolean to perform 'Receiver autonomous integrity monitoring' to detect and exclude observations that result in SPP failures.
\subsection{cycle\_slip:}
\subsubsection{thres\_slip:}
Threshold to apply to geometry free phase values to determine if an observation should be rejected due to a slip.
\subsection{max\_inno:}
Maximum innovation in PPP measurement before both phase and code measurements are excluded.
\subsection{deweight\_factor:}
Factor by which measurement variances are increased upon detection of a bad measurement.
\subsection{max\_gdop:}
Maximum 'geometric dilution of precision' allowed for an SPP result to be valid.
\subsection{antexacs:}
Internal processing option. Bad things will likely happen if this is set to false.
\subsection{sat\_pcv:}
Boolean to model satellite phase center variations.
\subsection{pivot\_station:}
Station specified as origin for receiver clocks. Clocks for this station will be constrained to zero. May be set to \textless AUTO \textgreater or undefined to use first available station.
\subsection{pivot\_satellite}:
Unused.
\subsection{wait\_next\_epoch:}
(under development)
Expected time interval between successive epochs data arriving. For real-time this should be set equal to epoch\_interval.
\subsection{wait\_all\_stations:}
(under development)
Window of delay to allow observation data to be received for processing.
Processing will begin at the earliest of: Observations received for all stations / wait\_all\_stations has elapsed since any station has received observations / wait\_all\_stations has elapsed since wait\_next\_epoch expired.

\subsection{code\_priorities:}
List of observation codes that may be used in processing, and the order of priority for use. (Currently only a single code is used per frequency)

\subsection{joseph\_stabilisation:}
Boolean to apply additional calculations in filter to ensure numerical stability.











\section{user\_filter\_parameters, network\_filter\_parameters, ionosphere\_filter\_parameters:}

\subsection{inverter:}
Method of inversion used to calculate kalman gain. options include 
LLT,
LDLT,
INV

\subsection{max\_prefit\_remvovals:}
Prior to kalman filtering the prefit residuals of measurements are checked for consistency, and may be removed or deweighted if not statistically reasonable. This parameter defines how many such measurements may be removed or deweighted at a given epoch.

These removals have low overhead associated with them as they occur before filter inversion takes place.

\subsection{max\_filter\_iterations:}
After kalman filtering, the postfit residuals of meaurements are checked for consistency, and measurements may be removed or deweighted if not statistically reasonable. This parameter specifies the number of times the filter may be iterated by deweighting and recomputing the resultant values.

These iterations have large overhead with them as the complete filter stage is computed multiple times. Large iteration values may exceed double the processing time.


\subsection{rts\_lag:}
Number of future epochs to use in RTS smoothing. A larger lag will give more optimal smoothing results, at the expense of a longer lag before they are calculated, and requiring more processing time per epoch.

A negative value indicates that the entire solution should be smoothed at the conclusion of processing. This will obtain optimal results, with lowest processing time, but is not suitable for real-time applications.

\subsection{rts\_directory:}
Directory to output RTS files.

\subsection{rts\_filename:}
Filename for RTS files. Multiple intermediate files are generated by RTS smoothing, as well as an additional output files for kalman filter states and clocks.

\subsection{outage\_reset\_limit:}
Maximum number of epochs with missed phase measurements before the ambiguity associated with the measurement is reset.

\subsection{phase\_reject\_limit:}
Maximum number of phase measurements to reject before the ambiguity associated with the measurement is reset.








\section{troposphere:}	TODO aaron, in config twice

\subsection{model:}

\subsection{vmf3dir:}

\subsection{orography:}

\subsection{gpt2grid:}




\section{ionosphere:}

\subsection{corr\_mode:}

\subsection{iflc\_freqs:}





\section{unit\_test\_options:}

\subsection{output\_pass:}

\subsection{stop\_on\_fail:}

\subsection{stop\_on\_done:}

\subsection{output\_errors:}

\subsection{absorb\_errors:}

\subsection{directory:}

\subsection{filename:}






\section{ionosphere\_filter\_parameters:}

\subsection{model:}

\subsection{lat\_center, lon\_center:}

\subsection{lat\_width, lon\_width:}

\subsection{lat\_res, lon\_res:}

\subsection{time\_res:}

\subsection{func\_order:}

\subsection{layer\_heights:}

\subsection{model\_noise:}





\section{ambiguity\_resolution\_options:}

\subsection{Min\_elev\_for\_AR:}

\subsection{Set\_size\_for\_lambda:}

\subsection{Max\_round\_iterat:}

\subsection{GPS\_amb\_resol:}

\subsection{WL\_mode:}

\subsection{WL\_succ\_rate\_thres:}

\subsection{WL\_sol\_ratio\_thres:}

\subsection{WL\_procs\_noise\_sat:}

\subsection{WL\_procs\_noise\_sta:}

\subsection{NL\_mode:}

\subsection{NL\_succ\_rate\_thres:}

\subsection{NL\_proc\_start:}

\subsection{read\_OSB:}

\subsection{read\_DSB:}

\subsection{read\_SSR:}

\subsection{read\_satellite\_bias:}

\subsection{read\_station\_bias:}

\subsection{read\_GLONASS\_IFB:}

\subsection{write\_OSB:}

\subsection{write\_DSB:}

\subsection{write\_SSR\_bias:}

\subsection{write\_satellite\_bias:}

\subsection{write\_station\_bias:}

\subsection{bias\_output\_rate:}






\section{minimum\_constraints:}

\subsection{process\_mode:}

\subsection{estimate:}

\subsubsection{scale:}

\subsubsection{rotation:}

\subsubsection{translation:}



\section{output\_options:}

\subsection{config\_description:}

\subsection{analysis\_agency:}

\subsection{analysis\_center:}

\subsection{analysis\_program:}

\subsection{rinex\_comment:}



\section{default\_filter\_parameters:}

\subsection{stations:}

\subsubsection{error\_model:}

\subsubsection{code\_sigmas, phase\_sigmas:}

\subsubsection{title}

\subsection{satellites:}

\subsection{eop:}




Receiver options - heirarchy


satellite options


Kalman objects

eigen

minimum constraint options

